A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-23 article/article.tex
update arch plot and finish ref section

@@

\cite{foretellix2019}

\cite{deGelder2022ontology}

\cite{wachenfeld2016release}

\cite{iso21448}

\cite{ul4600}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/graph_gine_architecture.pdf}
    \caption{Model architecture for the Graph Isomorphism Network with Edge features (GINE).}
    \label{fig:graph_gine_architecture}
\end{figure}

>>>>

In a similar direction, \cite{deGelder2022ontology} focus on defining ontoligies for automated vehicles
in an object oriented manner, with the intention to have a clearly defined and implementable
structures for scenarios, delivering a clear linkage to coverage arguments.

@@

A much more focussed example of coverage analysis in the context of autonomous driving is provided 
by \cite{foretellix2019} in a blog 
post, discussing topics like items, parameters and 
coverage buckets and performance metrics like time to collision and error collections.

The authors of (\cite{wachenfeld2016release}) investigate the significant challenge of safety validation and 
production release for fully autonomous vehicles, positing that established testing concepts are insufficient 
as they fundamentally rely on the human driver's ability to intervene as a safety backup. 
The authors introduce the "approval-trap," a statistical argument demonstrating the unfeasibility of proving 
superior safety through real-world driving, which would necessitate billions of test kilometers. 
This validation gap is presented as a fundamental problem of coverage analysis, where the
technical system must now demonstrably cover the vast operational domain previously managed by the 
human. The paper concludes that overcoming this challenge requires a paradigm shift toward new 
test case generation methodologies, such as critical scenario identification, and the extensive
 use of validated simulation-based tools to achieve sufficient test coverage efficiently.

Well known standards for coverage analysis in the context of autonomous driving are the 
ISO 21448 (\cite{iso21448}) and the UL 4600 (\cite{ul4600}).
The ISO 21448 is a standard for the safety of the intended functionality of road vehicles, 
including automated driving systems.
It defines a framework for coverage analysis, including the definition of coverage criteria and 
the measurement of coverage.
The UL 4600 is a standard for the safety of autonomous products, including automated driving systems.
It defines a framework for coverage analysis, including the definition of coverage criteria and the 
measurement of coverage.

@@

\begin{figure}[h]
    \centering
    %\includegraphics[width=0.8\textwidth]{plots/graph_gine_architecture.pdf}
    \includegraphics[width=0.8\textwidth]{plots/graph_gine_architecture_manually_updated.png}
    \caption{Model architecture for the Graph Isomorphism Network with Edge features (GINE).}
    \label{fig:graph_gine_architecture}
\end{figure}
